The Geometry of Archaeological Thought: Analysing discplinary change using word embeddings from conference abstracts

### 2020-05-07 documents/paper.Rmd
correct some typos

- word embeddings (cite our readings)
Word embeddings is useful tool based machine learning framework for measurement, quantifying, and comparing the semantic relations between words, which enables a wide range of application for temporal changes in word relationships related to the sociocultural domain [@Garg2018; @Kozlowski2019]. There are two major word-level pretrained word embeddings, Weod2Vec and Glove according to different methods [@Rong2014; @Pennington2014]. Since pretrained word embeddings are trained on large corpus such as Google News, they can capture the semantic meaning  of a word very well.

>>>>

- word embeddings (cite our readings)
Word embeddings is useful tool based machine learning framework for measurement, quantifying, and comparing the semantic relations between words, which enables a wide range of application for temporal changes in word relationships related to the sociocultural interests [@Garg2018; @Kozlowski2019]. There are two major word-level pretrained word embeddings, Word2Vec and Glove according to different methods used for training [@Rong2014; @Pennington2014]. Since pretrained word embeddings are trained on large corpus such as Google News, they can capture the semantic meaning of a word very well.
